Generating the Blueprints of the Maven Repository

### 2015-01-25 msr.tex
Fix my affiliation

\def\aueb{\textsuperscript{*}}
\def\tud{\textsuperscript{\dag}}

\author{
  Vassilios Karakoidas\aueb \and Dimitris Mitropoulos\aueb \and Panos Louridas\aueb \and Georgios Gousios\tud \and Diomidis Spinellis\aueb \\
  \begin{tabular}{ccc}
  \affaddr{\aueb Department of Management Science and Technology} & & \affaddr{\tud Software Engineering Research Group}\\
    \affaddr{\aueb Athens University of Economics and Business} & & \affaddr{\tud Delft University of Technology}\\
   \affaddr{Athens, Greece} & & \affaddr{Delft, the Netherlands}\\
   \email{\{bkarak,dimitro,louridas,dds\}@aueb.gr}& & \email{g.gousios@tudelft.nl} \\
  \end{tabular}
}

>>>>

\def\aueb{\textsuperscript{*}}
\def\run{\textsuperscript{\dag}}

\author{
  Vassilios Karakoidas\aueb \and Dimitris Mitropoulos\aueb \and Panos Louridas\aueb \and Georgios Gousios\run \and Diomidis Spinellis\aueb \\
  \begin{tabular}{ccc}
  \affaddr{\aueb Department of Management Science and Technology} & & \affaddr{\run Department of Digital Security}\\
    \affaddr{\aueb Athens University of Economics and Business} & & \affaddr{\run Radboud University Nijmegen}\\
   \affaddr{Athens, Greece} & & \affaddr{Nijmegen, the Netherlands}\\
   \email{\{bkarak,dimitro,louridas,dds\}@aueb.gr}& & \email{georgios@cs.ru.nl} \\
  \end{tabular}
}
